---
title:  "Biological reference points and projections"
subtitle: "Black sea bass Research Track"
author: 
  - "Tim Miller, Kierten Curti, Alex Hansell"
output:
  xaringan::moon_reader:
    self_contained: true
    css: ["xaringan-themer_16_9.css", "slides-style_TMB201.css"]
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


layout: true

.footnote[U.S. Department of Commerce | National Oceanic and Atmospheric Administration | National Marine Fisheries Service]


<style type="text/css">

code.cpp{
  font-size: 14px;
}
code.r{
  font-size: 14px;
}


</style>

```{css, echo=FALSE}
pre {
  max-height: 400px;
  max-width: 800px;
  overflow-y: auto;
}

```


```{r setup, include=FALSE}
#options(htmltools.dir.version = FALSE)
#library(knitr)
#knitr::opts_chunk$set(cache = TRUE)
#knitr::opts_knit$set(root.dir = here::here())
#library(kableExtra)
#library(imager)
#here::i_am("c:/work/BSB_RT")

library(here)

```

```{r xaringan-tile-view, echo=FALSE}
# this gives you a tile navigation if you type "O" at any time
#xaringanExtra::use_tile_view()
```

---
#Outline <br>

* General description of reference points in multi-stock extension of WHAM (TOR 5)
* BRPs for black sea bass application (TOR 5)
---

# Equilibrium per recruit calculations


The $n_r \times n_r$ matrix of equilibrium spawning stock biomass per recruit for stock $s$ in region $r'$ (columns) given recruiting in region $r$ (rows) is defined as
$$\widetilde {\mathbf{O}}_s({\widetilde F}) = \sum^{A}_{a=1} \mathbf{O}_{s,a} \mathbf{O}_{s,a}(\delta_s) \text{diag}\left({\bf f}_{s,a}\right)$$

where $\mathbf{O}_{s,a}(\delta_s)$ is $n_r x n_r$ is the matrix of probabilities of surviving and occurring in region $r'$ at age $a+\delta_s$ given starting in region $r$ at age $a$. It is the upper left sub-matrix of the probability transition matrix defined over the same interval. Similarly,
$$\mathbf{O}_{s,a} = \left\{ \begin{array}{ll} \prod^{a-1}_{i=0}\mathbf{O}_{s,i}  & 1\leq a<A\\ \left[\prod^{a-1}_{i=0}\mathbf{O}_{s,i}\right] \mathbf{O}_{s,+} & a = A \end{array}\right.$$
is the upper left sub-matrix of the probability transition matrix of states at age $a$ (columns) given being in each state (rows) at recruitment (age 1) where $\mathbf{O}_{s,0} = {\bf I}$. For the plus group $a=A$, $\mathbf{O}_{s,+} = \left(\mathbf{I} - \mathbf{O}_{s,A}\right)^{-1}$ is a "fundamental matrix" derived using the matrix version of the  geometric series. $\mathbf{f}_{s,a}$ is the vector of fecundities (product of weight and maturity) at age $a$ in each region. 


---

# Average FAA for black sea bass BRPs 

* Fishing mortality at age is averaged over last five years by fleet

```{r, echo = F, eval = T}
mod <- readRDS(here::here("2023.RT.Runs", "Run34", "fit_repmore.RDS"))
x <- round(mod$rep$FAA_static,2)
rownames(x) <- mod$input$fleet_names
colnames(x) <- mod$ages.lab
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
---

# Selectivity for black sea bass BRPs 

* Average fishing mortality at age and fleet is divided by the maximum of the total average FAA.

```{r, echo = F, eval = T}
x <- round(apply(mod$rep$FAA_static,2,sum),2)
names(x) <- mod$ages.lab
x <- knitr::kable(rbind(x), booktabs = T, escape=F, row.names = F)
knitr::knit_print(x)
```
$$\\[12pt]$$
```{r, echo = F, eval = T}
x <- round(mod$rep$FAA_static/apply(mod$rep$FAA_static,2,sum)[8],2)
rownames(x) <- mod$input$fleet_names
colnames(x) <- mod$ages.lab
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
---

# Weight at age for black sea bass BRPs

* Weight at age for SSB and fleets are averaged over last 5 years

```{r, echo = F, eval = T}
x<- round(mod$rep$waa_ssb_static, 2)
rownames(x) <- mod$input$stock_names
colnames(x) <- mod$ages.lab
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
$$\\[12pt]$$
```{r, echo = F, eval = T}
x<- round(mod$rep$waa_catch_static, 2)
rownames(x) <- mod$input$fleet_names
colnames(x) <- mod$ages.lab
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
---

# Maturity and M at age for black sea bass BRPs

```{r, echo = F, eval = T}
x<- round(mod$rep$mature_static, 2)
rownames(x) <- mod$input$stock_names
colnames(x) <- mod$ages.lab
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
$$\\[12pt]$$
```{r, echo = F, eval = T}
x<- round(exp(mod$rep$log_M_static)[,1,], 2)
rownames(x) <- mod$input$stock_names
colnames(x) <- mod$ages.lab
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
---

# Unfished equlibrium survival for black sea bass BRPs (North)

.pull-left[
Recruits
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,1,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
Age 2
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,2,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
]

.pull-right[
Age 3
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,3,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
Age 4
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,4,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
]

---

# Unfished equlibrium survival for black sea bass BRPs (North)

.pull-left[
Age 5
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,5,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
Age 6
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,6,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
]

.pull-right[
Age 7
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,7,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
Age 8
```{r, echo = F, eval = T}
x<- round(mod$rep$NAAPR0_static[1,8,,], 2)
rownames(x) <- mod$input$region_names
colnames(x) <- mod$input$region_names
x <- knitr::kable(x, booktabs = T, escape=F, row.names = T)
knitr::knit_print(x)
```
]

---

# Proportions at age
```{r, echo = FALSE, fig.dim =c(8,5), fig.align="center"}
par(mfrow = c(1,2), oma = c(4,4,0,0),mar = c(1,2,3,1))
stock <- c("North", "South")
for(i in 1:2){
	propAA0 <- mod$rep$NAAPR0_static[i,,i,i]
	propAA0 <- propAA0/sum(propAA0)
	propAAF40 <- mod$rep$NAAPR_FXSPR_static[i,,i,i]
	propAAF40 <- propAAF40/sum(propAAF40)
	propAA_term <- mod$rep$NAA[i,i,33,]
	propAA_term <- propAA_term/sum(propAA_term)

	plot(1:8, propAA0, ylim = c(0,0.45), xaxt = "n", ylab = "", type = 'n', xlab = "")
	grid(col = gray(0.7))
	lines(1:8,propAA0)
	lines(1:8, propAAF40, lty = 2)
	lines(1:8, propAA_term, col = "blue")
	axis(1, at = 1:8, labels = mod$ages.lab)
	if(i == 1) legend("topright", legend = c("Equilibrium unfished", "Equilibrium at F40", "2021"), col = c("black","black", "blue"), lty = c(1,2,1))
	mtext(side = 3, stock[i], line = 0, outer = F)
}
mtext(side = 1, outer = T, "Age", line = 2.5)
mtext(side = 2, outer = T, "Proportion", line = 2.5)
```

---

layout: false
class: middle, center

# Projections (TOR 6)


---

layout: true


---
